Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 Discussion-Proof.tex
fix a typo

\begin{rtheorem}{Theorem}{\ref{rst:known-p}}
Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has an expected payment bounded above by 
$\pfedit{O\left(N^2 \max\{1, (L/p)^{5/2}\}\right)}$.
and an expected regret bounded above by
\bcedit{
\begin{align*}
O \left(\frac{\MAXR \ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
  + \frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right).
\end{align*}
}
\end{rtheorem}

\begin{proof}
	The proof of the expected payment bound follows Lemma~\ref{rst:budget} \pfedit{ except we define 
	$h(\ell)$ without including the $\exp(2/\MinProb)$ term}
    as $h(\ell) := \max\big\{ \left(\frac{24\sigma \ell\Diam d}{\TieCutoff} \right)^{5/2},
        \left( \frac{48\sigma \ell\TieDensity \Diam d}{\MinProb} \right)^{5/2}\big\}$
\pfedit{
The resulting bound on expected payment is
$O\left(\ARMNUM^2 d\cdot(R+Dd\sigma)\cdot \max\bigg\{ \left(\frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2},
 \left( \frac{\sigma \TieDensity \Diam d}{\MinProb} \right)^{5/2}\bigg\}\right)
 = O\left(N^2 \max\{1, (L/p)^{5/2}\}\right)$.
}

The proof of the expected regret bound first establishes tightened versions of Lemmas~\ref{lem:no-incentives} and \ref{lem:numP},
proving the following upper bound on the number of time steps in which a payment is made:
\begin{align}
O\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
  + \frac{\ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right). \nonumber 
\end{align}
The proof of this result follows that of Lemma~\ref{lem:numP},
but the less aggressive incentivization allows us to define $\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3})$ since $\frac{1}{\log(s+s_0)} \leq \frac{\MinProb}{2}$ is true for all $s$.

>>>>

\begin{rtheorem}{Theorem}{\ref{rst:known-p}}
Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has an expected payment bounded above by 
$\pfedit{O\left(N^2 \max\{1, (L/p)^{5/2}\}\right)}$.
and an expected regret bounded above by
\bcedit{
\begin{align*}
O\left(\frac{\ARMNUM^2}{\MinProb^2}
    + \frac{\ARMNUM^2}{\hat{z}^2} + \frac{\ARMNUM}{\hat{z}^3}
    + \frac{NL\log^3(T)}{p}    
    \right)
\end{align*}
}
\end{rtheorem}

\begin{proof}
	The proof of the expected payment bound follows Lemma~\ref{rst:budget} \pfedit{ except we define 
	$h(\ell)$ without including the $\exp(2/\MinProb)$ term}
    as $h(\ell) := \max\big\{ \left(\frac{24\sigma \ell\Diam d}{\TieCutoff} \right)^{5/2},
        \left( \frac{48\sigma \ell\TieDensity \Diam d}{\MinProb} \right)^{5/2}\big\}$.
\pfedit{
The resulting bound on expected payment is
$O\left(\ARMNUM^2 d\cdot(R+Dd\sigma)\cdot \max\bigg\{ \left(\frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2},
 \left( \frac{\sigma \TieDensity \Diam d}{\MinProb} \right)^{5/2}\bigg\}\right)
 = O\left(N^2 \max\{1, (L/p)^{5/2}\}\right)$.
}

The proof of the expected regret bound first establishes tightened versions of Lemmas~\ref{lem:no-incentives} and \ref{lem:numP},
proving the following upper bound on the number of time steps in which a payment is made:
    \bcedit{
\begin{align}
O\left(\frac{\ARMNUM^2 \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^2}
    + \frac{\ARMNUM^2 d^3 \sigma^2 \Diam^2}{\hat{z}^2} + \frac{\ARMNUM \Diam^3 d^3 \sigma^3}{\hat{z}^3}
 \right). \nonumber 
\end{align}
}
The proof of this result follows that of Lemma~\ref{lem:numP},
but the less aggressive incentivization allows us to define $\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3})$ since $\frac{1}{\log(s+s_0)} \leq \frac{\MinProb}{2}$ is true for all $s$.
